Joint Satellite Distributions in the Local Group

### 2017-10-03 paper/paper.tex
new plots
+1 paragraph

@@

We test the shape and alignment statistics for 11 up 25 satellites.
The lowest number corresponds to the number of classical Milky Way
satellites.
We compare the resuls of the satellite distributions with the average
of from 10000 randomized version of the same satellites.
The spherical randomization is done as described in Section X.

Figure \ref{fig:general} summarized the results. 
The left column shows

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.40\textwidth]{LG_scatter_width.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_mu.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ca_ratio.pdf}
\includegraphics[width=0.40\textwidth]{LG_scatter_ba_ratio.pdf}
\caption{Basic characteristics for the MW and M31 satellite systems
\label{fig:sampling}}
\end{figure*}

@@

We test the shape and alignment statistics for 11 up 15 satellites.
The lowest number corresponds to the number of classical Milky Way
satellites.
The upper limit corresponds to the minimum number of satellites that
can be resolved in the simulations for both halos in each pair. 
In the case of simulations we rank the subhalos by their maximum
circular velocity. 
We do not use their stellar properties because this represents the
lower resolution limit for the hydrodynamics; most of these subhalos
only have one stellar particle belonging to them. 
In contrast, the detected sub-halos have at least 35 dark matter
particles to determine their properties.

We build two different kinds of statistics from these satellites
First, we compute the shape and alignments for a varying number of
satellites $11\leq N_{s}\leq 15$ keeping their ranking in
$V_{mag}$/$V_{max}$. 
This allows us to estimate the variation expected by changing the
satellite number. 
The second kind of statistics are computed for a fixed number of
satellites $N_{s}=11$ randomly selected from the top $15$ ranked
satellites. 
We perform this bootstrapping $10$ times for each pair. 
This allows us to estimate the variation expected by randomly sampling
the satellites from a parent distribution.

Figure \ref{fig:sampling} summarized the results.
